This file contains the questions that will be asked to the participants

\section{Before the Experiment}
- What is your name? (use unique name, do not have to be your real name)

- How old are you? <12, 12-27, 28-43, 44-59, 60-69, >69

- How do you evaluate your knowledge about sharks?
Excellent
Good
Average
Bad
Terrible

- Name your mother language(s)?

- What is the order of English in the languages you know? (second language learned ...)

- Did you ever meet/have a conversation with a robot? if yes who?

\section{After the Experiment}
The 'v' indicating the right answer will, of course, be removed from the question when it is asked to the participants.

What is your name? (same unique name of the first questioner) 
\subsection{question about the lecture}
1. What is the text about?
a. whales
b. fishes
c. sharks v
d. electric eel

2. What is the age of sharks on Earth?
a. 440 thousand years
b. 500 million years
c. 400 million years v
d. 550 thousand years

3. To which class do sharks belong?
a. Chondrichthyes v
b. Arthropods
c. Echinoderms
d. Mammals

4. How many shark species are there?
a. over 500 thousand species
b. over 500 species v
c. over 600 species
d. over 400 species

5. What allows the unique head shape of the hammerhead shark mentioned in the lecture?
a. better sensory perception v
b. efficient predator
c. entering places other shark species cannot enter
d. nothing from above

6. Which of these sentences is correct?
a. cartilage is heavier and more flexible than bone
b. cartilage is lighter and less flexible than bone
c. cartilage is heavier and less flexible than bone
d. cartilage is lighter and more flexible than bone v

7. How many rows of teeth in total does the bull shark have according to the lecture?
a. 15 rows in each jaw
b. 50 rows in each jaw v
c. 5 rows in each jaw
d. 100 rows in each jaw

8. Which of these sentences is true according to the lecture?
a. sharks can feel the vibration and movement in the water v
b. sharks do not have a good hearing ability
c. sharks can smell blood from just a few meters
d. sharks can see their prey from kilometers away

9. According to the lecture, which of these is a reason for overfishing sharks?
a. making soup from shark fin v
b. making clothing
c. making necklaces from the teeth of sharks
d. for fun

10. Which of these types is often referred to as a "living fossil"?
a. the wobbegong shark
b. the goblin shark
c. The frilled shark v 
d. the Greenland shark

\subsection{Questions about the robot}

1. How did you feel about taking a lesson from a robot?
Loved it
Liked it
It was okay
Disliked it
Hated it

2. Are you interested in trying this more in the future?
Definitely
Probably
Not sure
Probably not
Definitely not

3. Would you choose to take a lesson from a robot over a human teacher?
Yes, definitely
Yes, probably
Not sure
No, probably not
No, definitely not

4. Do you have any extra notes?